Measuring sustainability with Australian vine growers using a Bayesian Network

### 2024-02-08 article.tex
abstract (and other files not uploaded?)

>>>>

% Abstract

Title:
A Bayesian Network Model based decision support tool for Environmental Sustainability in the Australian Winegrowing Industry.

Abstract:

The assessment of environmental sustainability in the Australian winegrowing industry remains a complex issue involving changing and compounding factors. To address this, we developed a Bayesian Network (BN) using data and expert elicitation to summarise the key factors, their relationships, and how they come together to influence vineyards' environmental outcomes. The study leveraged diverse expert perspectives to mitigate biases in probability estimations and promote discourse.

The development of the BN involved an iterative process, including variable selection and definition, the defining of model structure and variable relationships, and finally the determining of relationship significance through probabilities. Expert input was pivotal in structuring the BN model, ensuring relevance to industry, and how a variables influence changed across regions and scenarios.

Due to the possible variation in any given vineyard scenario the BN model was expanded to review a case study of the Coonawarra wine region in South Australia. This highlighted regional differences between growers whilst also maintaining the significance of industry-wide concerns such as the use of agrochemicals. To promote accessibility and scrutiny the BN was further developed into an application, allowing the possibility of further industry and stakeholder feedback; enabling a systematic re-evaluation of significant factors to the wine growing industry and how they change over time.
